---
title: "MA_Regressions"
author: "Monique Bennett"
date: "16/01/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=F, error=F, message=F}
library(car)
library(stargazer)
library(effects)
library(readxl)
library(dplyr)
library(xtable)
library(tikzDevice)
library(wordcloud)
library(jtools)
```

```{r}
load("MA_DATASET.RData")

row.names(wb_epi_df) <- wb_epi_df$iso3c


```

### Summary Table

```{r}
sum_df <- data.frame(wb_epi_df$EPI2018Score, wb_epi_df$lied_dummy, 
                     wb_epi_df$VA.EST, wb_epi_df$PV.EST,wb_epi_df$GE.EST, 
                     wb_epi_df$RQ.EST, wb_epi_df$RL.EST, wb_epi_df$CC.EST, 
                     wb_epi_df$resource_rents_log, wb_epi_df$trade_log, 
                     wb_epi_df$GDP.lpc, log(wb_epi_df$PopDensity))

names(sum_df) <- c("EPI", "Democracy dummy", "Voice and Accountability",
                   "Political stability","Gov Effectiveness", 
                   "Regulatory Quality", "Rule of Law", "Corruption",
                   "log(Resource Rents)", "log(Trade Open)", "log(GDPpc)", "log(PopDensity)")

summary(sum_df)
```

```{r results='asis'}
stargazer(sum_df, type = "latex", digits = 2, float = F, title = "Descrptive Statistics", summary.stat = c("mean", "median","sd","min", "max","n"))
```

### Correlation Matrix
```{r results='asis'}

cor.df <- data.frame(wb_epi_df$EPI2018Score, wb_epi_df$lied_dummy, 
                     wb_epi_df$VA.EST, wb_epi_df$PV.EST,wb_epi_df$GE.EST, 
                     wb_epi_df$RQ.EST, wb_epi_df$RL.EST, wb_epi_df$CC.EST, 
                     wb_epi_df$resource_rents_log, wb_epi_df$trade_log, 
                     wb_epi_df$GDP.lpc, log(wb_epi_df$PopDensity))


names(cor.df) <- c("EPI", "LIED", "VA", "PV", "GE", "RQ", "RL", "CC", "Resource_rents", "Trade", "GDPpc", "PopDlog")

cor.mat <- round(cor(cor.df, use = "complete.obs"), digits = 2)
upper.cor <- cor.mat
upper.cor[upper.tri(cor.mat)] <- ""
upper.cor <- as.data.frame(upper.cor)
upper.cor

stargazer(round(cor(cor.df, use = "complete.obs"), digits = 2))

```

## Regressions
### LM VA

```{r}
lm.1 <- lm(EPI2018Score ~ VA.EST + lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

plot(allEffects(lm.1, ask=T))

par(mfrow=c(2, 2))
plot(lm.1)
```

### LM PV

```{r}
lm.2 <- lm(EPI2018Score ~ PV.EST + lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

plot(allEffects(lm.2, ask=FALSE)) # effects plot

par(mfrow=c(2, 2))
plot(lm.2)
```

### LM Gov Effectiveness

```{r}
lm.3 <- lm(EPI2018Score ~ GE.EST + lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

plot(allEffects(lm.3, ask=FALSE)) # effects plot

pdf(file = "effect plot GE", width = 6, height = 4.3)
effect_plot(lm.3, pred = GE.EST, interval = T, plot.points = T, main.title = "Effect of government effectiveness on EPI scores",  jitter = 0.1, data = wb_epi_df)
dev.off()

par(mfrow=c(2, 2))
plot(lm.3)
```

### LM Reg Quality

```{r}
lm.4 <- lm(EPI2018Score ~ RQ.EST  + lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

plot(allEffects(lm.4, ask=FALSE))

par(mfrow=c(2, 2))
plot(lm.4)
```

## RL

```{r}
lm.5 <- lm(EPI2018Score ~ RL.EST  + lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

plot(allEffects(lm.5, ask=FALSE))

par(mfrow=c(2, 2))
plot(lm.5)
```

### Political Violence

```{r}
lm.6 <- lm(EPI2018Score ~ CC.EST  + lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

plot(allEffects(lm.6, ask=FALSE))

par(mfrow=c(2, 2))
plot(lm.6)
```

### Only dummy

```{r}
lm.7 <- lm(EPI2018Score ~ lied_dummy + trade_log + 
               log(NY.GDP.PCAP.CD) + resource_rents_log + log(PopDensity), 
           data = wb_epi_df)

par(mfrow=c(2, 2))
plot(lm.7)
```

## Regression Table

```{r results='asis'}
stargazer(lm.1, lm.2, lm.3, lm.4, lm.5, lm.6, type = "latex", 
          digits = 2, float = F,  no.space = TRUE, column.sep.width = "1pt", font.size = "small")
```

### Regression Plots

#### VA avPlot
```{r}
avPlot(lm.1, variable = "VA.EST", id = TRUE)
```

#### PV
```{r}
avPlot(lm.2, variable = "PV.EST", id = TRUE)
```

#### Government Effectiveness 
```{r}
pdf(file = "avPlot_GE", width = 10, height = 8)
avPlot(lm.3, variable = "GE.EST", 
       id=list(n=101, cex=1, col=carPalette()[1], 
               col.lines = carPalette()[2], location="lr"))
dev.off()

textplot( words = "iso3c", new = T)

list(abs(residuals(lm.3, type="pearson")), "x")

pdf(file = "avPlot_gdp_GE.pdf")
avPlots(lm.3, terms = "log(NY.GDP.PCAP.CD)", id=list(n=101, cex=1, col=carPalette()[1], col.lines = carPalette()[2], location="lr"))
dev.off()

summary(wb_epi_df)


plot(GE.EST ~ EPI2018Score, data = wb_epi_df)
abline(lm(GE.EST ~ EPI2018Score, data = wb_epi_df))

    ```

    ##### Regulatory Quality
```{r}

pdf(file = "avPlot_RQ", width = 8, height = 11)
avPlot(lm.4, variable = "RQ.EST", id=list(n=51, cex=1, col=carPalette()[1], location="lr"))
dev.off()

pdf(file = "avPlot_gdp_RQ", width = 8, height = 11)
avPlots(lm.4, terms = "log(NY.GDP.PCAP.CD)", id=list(method=list(abs(residuals(lm.4, type="pearson")), "x"), n=101, cex=1, col=carPalette()[1], location="lr"))
dev.off()

```

#### Control of Corruption
```{r}
avPlot(lm.5, variable = "CC.EST", id = TRUE)
```

#### Political Violence
```{r}
avPlot(lm.6, variable = "PV.EST", id = TRUE)
```

#### LIED 
```{r}
avPlot(lm.7, variable = "lied_dummy", id = TRUE)
```
### Influence Plots
#### LM Rule of Law
```{r}
influencePlot(lm.1, id=list(n=3, cex=0.6))
```

#### LM Voice and Acc 
```{r}
influencePlot(lm.2)
```

#### LM Gov Effectiveness
```{r}
influencePlot(lm.3)
```

#### LM Regulatory Quality
```{r}
influencePlot(lm.4) 
```

#### LM Corruption
```{r}
influencePlot(lm.5)
```

#### LM Political Violence
```{r}
influencePlot(lm.6)

```

#### LM Only dummy
```{r}
influencePlot(lm.7)
```

## Residual Plots
#### LM RL
```{r}
par(mfrow=c(2, 2)) 
residualPlots(lm.1, cex=0.5, test=FALSE, layout=NA, ask=FALSE)
```
#### LM VA

```{r}
par(mfrow=c(2, 2)) # by default one per predictor + fitted values
residualPlots(lm.2, cex=0.5, test=FALSE, layout=NA, ask=FALSE)
```

#### LM GE
```{r}
par(mfrow=c(2, 2)) 
residualPlots(lm.3, cex=0.5, test=FALSE, layout=NA, ask=FALSE)
```

#### LM RQ
```{r}
lm.3a <- lm(EPI2018Score ~ GE.EST + lied_dummy + trade_log + log(NY.GDP.PCAP.CD) +
              resource_rents_log, data = wb_epi_df)

plot(lm.3a)
plot(lm.3)

anova(lm.3, lm.3a)
par(mfrow=c(2, 2)) 
residualPlots(lm.3, cex=0.5, test=FALSE, layout=NA, ask=FALSE)
```

#### LM CC
```{r}
par(mfrow=c(2, 2)) # by default one per predictor + fitted values
residualPlots(lm.4, cex=0.5, test=FALSE, layout=NA, ask=FALSE)
```

### NCVTEST
```{r}
ncvTest(lm.1)
```

```{r}
ncvTest(lm.2)
```

```{r}
ncvTest(lm.3)
```

```{r}
ncvTest(lm.4)
```

```{r}
ncvTest(lm.5)
```

```{r}
ncvTest(lm.6)
```

```{r}
ncvTest(lm.7)
```

### ANOVA

```{r}

```

